Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2022-04-25 Paper/Paper.tex
Updates from Overleaf

Second, I assume physicians do not anticipate EHR exposure prior to occurrence. Since the technology has different vendors and varies in capabilities, anticipation may be a concern if physicians learn that the system will be implemented and then do not actually use it until a future period. Generally, even a complex EHR system can be completely set up within a year, and most systems take 6 to 9 months (\cite{uzialko_2021}). Therefore, I proceed in the main specification assuming no anticipation. However, I explore and present results for a one year anticipation period in Appendix ().

@@

\subsection{Anticipation}

@@

\begin{figure}
    \centering
    \caption{Comparison of ATT, Main Specification and Low-Integration Treatment Variable}
    \includegraphics[scale=.5]{Objects/LI_results.pdf}
    \label{fig:LI}
\end{figure}

>>>>

Second, I assume physicians do not anticipate EHR exposure prior to occurrence. Since the technology has different vendors and varies in capabilities, anticipation may be a concern if physicians learn that the system will be implemented and then do not actually use it until a future period. Generally, even a complex EHR system can be completely set up within a year, and most systems take 6 to 9 months (\cite{uzialko_2021}). Therefore, I proceed in the main specification assuming no anticipation. However, I explore and present results for a one year anticipation period in Appendix \ref{app:anticipation}.

@@

\subsection{Anticipation}\label{app:anticipation}

While there is evidence to suggest the time it takes to implement an EHR does not exceed one year, there still may be some anticipation if physicians are expecting implementation in the hospitals they work in. In Figure \ref{fig:anticipation}, I present aggregated estimates in the case of one year of anticipation. The results are virtually identical, just noisier, compared to the estimates from the main specification.

\subsection{Other Estimators}

@@

\begin{figure}[ht]
    \centering
    \caption{Comparison of ATT, Low-Integration Treatment Variable}
    \includegraphics[scale=.5]{Objects/LI_results.pdf}
    \label{fig:LI}
\end{figure}

\begin{figure}[ht]
    \centering
    \caption{ATT With Anticipation}
    \includegraphics[scale=.57]{Objects/anticipation_graph.pdf}
    \label{fig:anticipation}
\end{figure}
